### 2023-02-24 chapter0/chapter0.tex
Updated section formatting in remaining files
Added discussion of structure to introduction

@@

Many studies investigated various structural and functional aspects of IDRs and IDPs followed in the following years.

>>>>

\section{Background}

@@

Over the following years, many studies investigated the structural and functional properties of IDRs. They found that although IDRs still have sequence-structure-function relationships, they play by a very different set of rules. These differences manifest at all three levels but are at first most easily understood in terms of structure. Strictly speaking, a protein's structure refers its three-dimensional arrangement of atoms. Thus, ``structured'' regions in proteins, called domains\footnote{Though there are various overlapping definitions, domains typically refer to independently folding regions of a protein. Domains are also described as discrete functional or evolutionary elements since proteins may contain several domains which are connected by unstructured ``linker'' sequences.}, typically adopt a small number of structures. This does not imply structured domains are completely rigid, though. At the molecular level, everything is in constant motion. For example, at room temperature an average water molecule moves at over 500 meters per second! However, the aqueous environment is so dense that it will collide with something after moving only a fraction of its own length. Structured domains are buffeted by these collisions with water and other molecules, but they are constrained by the rigid bonds and interactions between amino acid residues in the chain. Thus, while structured domains can ``flex'' and ``breathe,'' these motions are minor variations on their overall structure.

In some cases, structured domains have multiple structures, or ``conformations,''  which are related to different functional states. For example, hemoglobin has two forms, traditionally called the T and R states. The T state is hemoglobin's oxygen-free form, but on binding oxygen its structure shifts to the R state. The change is small, differing only by a few hydrogen atoms at the points of greatest change. However, this enough to re-orient the atoms that interact with oxygen, allowing it to bind more tightly and promoting oxygen uptake at the other three binding sites. Once the red blood cells reach their destination, other physiological factors favor the adoption of the T state, which coordinates the release of all four oxygen atoms. Thus, when structured domains have multiple conformations, they are generally discrete forms without stable intermediates.

In contrast, IDRs have no fixed spatial relationship between their atoms and are sometimes described as ``conformational ensembles,'' \textit{i.e.} a collection of related structures.

\section{Aims}

This is where my aims will go!
